### 2016-03-15 paper/result_layered_depthmap.tex
Hang

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
    \caption{}
    \label{fig:layered_depthmap_by_alpha}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_N.png}
    \caption{}
    \label{fig:layered_depthmap_by_N}
  \end{subfigure}
  \caption{(a) Energy plots for layered depthmap estimation with varying
    $\alpha$. (b) Energy plots for layered depthmap estimation with varying number of threads N.}
  \label{fig:layered_depthmap_by_alpha_N}
\end{figure}

%
% From the plot, we can see that, Fusion Move, Parallel Fusion Move, and
%SF-MF all stalk at a high energy state.
To further study the effects of multi-way fusion, we have varied the
value of $\alpha$ which controls the number of solution proposals to be
fused in SF-SS model (See
Fig.~\ref{fig:layered_depthmap_by_alpha}). Note that we have used SF-SS
instead of SF to disable solution sharing and better observe the effects
of multi-way fusion.
% SF-SS model (disable solution sharing to
%better observe the effect of multi-way fusion) while keeping other
%parameters the same and plot the energy minimization process in figure
It is interesting to see that more multi-way fusion takes longer to
converge, but finds a lower energy state at the end.

Finally, we have examined the role of multi-threading by varying the
number of threads N in our most general model SF (See
Fig.~\ref{fig:layered_depthmap_by_N})~\footnote{While keeping other
parameters the same, we have to change $\beta$ with $N$ because of the
constraint $\beta \leq N-1$. We have always used $\beta = N-1$ in this
experiment.}. More threads lead to faster convergence as expected,
although the rate of speed-up is not proportional to the number of
threads due to the randomness in the proposal generation scheme.
%The plot shows that SF finds low energy faster with more
%threads.
% In Fusion Move like methods, parallelism speeds up convergence
% by exploring solution proposals faster. Due to the inherited randomness
% in the proposal generation scheme, the speed up is often not
% proportional to the number of threads.
%We can see that as the number of
%ways to fuse becomes larger, each fusion step takes longer time, but the
%chance of finding a lower energy state increases.

>>>>

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_N.png}
  \end{subfigure}
  \caption{(a) Energy plots for layered depthmap estimation with varying
    $\alpha$. (b) Energy plots for layered depthmap estimation with varying number of threads N.}
  \label{fig:layered_depthmap_configuration}
\end{figure}

%
% From the plot, we can see that, Fusion Move, Parallel Fusion Move, and
%SF-MF all stalk at a high energy state.
To further study the effects of multi-way fusion, we have varied the
value of $\alpha$ which controls the number of solution proposals to be
fused in SF-SS model (See
Fig.~\ref{fig:layered_depthmap_configuration}(left)). Note that we have used SF-SS
instead of SF to disable solution sharing and better observe the effects
of multi-way fusion.
% SF-SS model (disable solution sharing to
%better observe the effect of multi-way fusion) while keeping other
%parameters the same and plot the energy minimization process in figure
It is interesting to see that more multi-way fusion takes longer to
converge, but finds a lower energy state at the end.

Finally, we have examined the role of multi-threading by varying the
number of threads N in our most general model SF (See
Fig.~\ref{fig:layered_depthmap_configuration}(right))~\footnote{While keeping other
parameters the same, we have to change $\beta$ with $N$ because of the
constraint $\beta \leq N-1$. We have always used $\beta = N-1$ in this
experiment.}. More threads lead to faster convergence as expected,
although the rate of speed-up is not proportional to the number of
threads due to the randomness in the proposal generation scheme.
%The plot shows that SF finds low energy faster with more
%threads.
% In Fusion Move like methods, parallelism speeds up convergence
% by exploring solution proposals faster. Due to the inherited randomness
% in the proposal generation scheme, the speed up is often not
% proportional to the number of threads.
%We can see that as the number of
%ways to fuse becomes larger, each fusion step takes longer time, but the
%chance of finding a lower energy state increases.

### 2016-03-15 paper/result_optical_flow.tex
Hang

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_PFM_threads.png}
    \caption{}
    \label{fig:optical_flow_PFM_threads}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_SF_MF_threads.png}
    \caption{}
    \label{fig:optical_flow_SF_MF_threads}
  \end{subfigure}
  \caption{Energy plots per thread for (a) Parallel Fusion  
    Move (PFM) and (b) our SF-MF.}
  \label{fig:optical_flow_by_threads}  
\end{figure}

@@

There are two factors influencing solution sharing: 1) \textit{the
number of solutions to share} and 2) \textit{the frequency of solution
sharing}. Both factors are controlled by $\beta$. As mentioned in
Section~\ref{section:algorithm}, we have used $\beta = 1$ (i.e., share
solutions) once in every five iterations.  To further understand the
effects of solution sharing, we conducted two more experiments. First,
we set $\beta$ to 0, 1, 2, or 3 in every five iterations,
% (when $\beta = 0$, it is the same with PFM without final merging).
while keeping all other parameters the same (See
Fig.~\ref{fig:optical_flow_by_beta}).  Second, we change the number of
iterations $k$ between the two consecutive solution sharing iterations
(See Fig.~\ref{fig:optical_flow_by_interval}).  The first experiment
revealed that the solution sharing makes convergence faster regardless of
$\beta$.  However, too much solution sharing slows down the convergence,
and $\beta=1$ is the sweet spot for this problem.
%
% , energy generally
% decreases faster with solution sharing. But since we need to perform one
% fusion for sharing each solution, sharing more solution decreases
% efficiency in this problem setting. While sharing multiple solutions
% might be useful in some other problem setting as it means each thread
% can get more global information early.
%
The second experiment has shown that too frequent solution sharing
harms the convergence, simply because threads have less time generating more
proposals and exploring the solution space.
% From this figure, we can see that
% although solution sharing generally speeds up the optimization process,
% sharing solution too frequently is not a good practice. This is because
% when we share solution frequently, we have less time for generating and
%fusing new proposals.
Optimal parameter setting depends on each problem setting.
%A good choice of the solution sharing frequency depends on specific
%problem setting.

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
    \caption{}
    \label{fig:optical_flow_by_beta}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
    \caption{}
    \label{fig:optical_flow_by_interval}
  \end{subfigure}
  \caption{Energy plots for optical flow with (a) varying
    $\beta$ and (b) varying solution sharing
    frequencies. Solution sharing achieves better convergence, but sharing too many solutions (larger $\beta$) or sharing solutions too frequently (less $k$) slows down the convergence, as it reduces the time for exploration.}
\end{figure}

>>>>

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_PFM_threads.png}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_SF_MF_threads.png}
  \end{subfigure}
  \caption{Energy plots per thread. Left: Parallel Fusion  
    Move (PFM). Right: SF-MF(ours).}
  \label{fig:optical_flow_by_threads}  
\end{figure}

@@

There are two factors influencing solution sharing: 1) \textit{the
number of solutions to share} and 2) \textit{the frequency of solution
sharing}. Both factors are controlled by $\beta$. As mentioned in
Section~\ref{section:algorithm}, we have used $\beta = 1$ (i.e., share
solutions) once in every five iterations.  To further understand the
effects of solution sharing, we conducted two more experiments. First,
we set $\beta$ to 0, 1, 2, or 3 in every five iterations,
% (when $\beta = 0$, it is the same with PFM without final merging).
while keeping all other parameters the same (See
Fig.~\ref{fig:opticalflow_configuration}(left)).  Second, we change the number of
iterations $k$ between the two consecutive solution sharing iterations
(See Fig.~\ref{fig:opticalflow_configuration}(right)).  The first experiment
revealed that the solution sharing makes convergence faster regardless of
$\beta$.  However, too much solution sharing slows down the convergence,
and $\beta=1$ is the sweet spot for this problem.
%
% , energy generally
% decreases faster with solution sharing. But since we need to perform one
% fusion for sharing each solution, sharing more solution decreases
% efficiency in this problem setting. While sharing multiple solutions
% might be useful in some other problem setting as it means each thread
% can get more global information early.
%
The second experiment has shown that too frequent solution sharing
harms the convergence, simply because threads have less time generating more
proposals and exploring the solution space.
% From this figure, we can see that
% although solution sharing generally speeds up the optimization process,
% sharing solution too frequently is not a good practice. This is because
% when we share solution frequently, we have less time for generating and
%fusing new proposals.
Optimal parameter setting depends on each problem setting.
%A good choice of the solution sharing frequency depends on specific
%problem setting.

\begin{figure}[!h]
\centering
\begin{subfigure}[b]{0.49\columnwidth}
\includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
\end{subfigure}
\begin{subfigure}[b]{0.49\columnwidth}
\includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
\end{subfigure}
\caption{Energy
  plots for optical flow under difference configurations. Left:
  varying $\beta$; right: varying solution sharing
  frequencies. Solution sharing achieves better convergence, but
  sharing too many solutions (larger $\beta$) or sharing solutions too
  frequently (less $k$) slows down the convergence, as it reduces the
  time for exploration.}
  \label{opticalflow_configuration}
\end{figure}
